### 2020-06-02 report/sections/server/codegen/workflow.tex
Report: minor changes  to background and workflow

We motivate our development workflow from previous work 
\cite{PureScript2019} by extending the Scribble toolchain
and generating APIs that integrate the developer's 
application logic
into the execution of the communication automata.

>>>>

We motivate our development workflow from previous work 
\cite{PureScript2019, Hybrid2016} by extending the Scribble toolchain
and generating APIs that integrate the developer's 
application logic
into the execution of the communication automata.
